---
title: "01-data-exploration"
author: "Ana Olsen"
date: "11/18/2020"
output: html_document
---

First I loaded necessary packages.
```{r, warning = FALSE, message = FALSE}
library(dplyr)
library(ggplot2)
```

Then I read in the .csv data files from Figshare. The experiment data I'm using came from a paper called "Consistent diferences in Fitness Traits across Multiple Generations of Olympia Oysters", listed as "F2 Puget Sound Olympia Oyster Population Structure" on Figshare. It was created by Katherine Silliman, Tynan Bowyer, and Steven Roberts.

```{r}

PS_larvae <- read.csv("../raw_data/Copy of PS_Larvae.csv")
oyster_tile_size <- read.csv("../raw_data/Copy of Oyster Tile Size Data.csv")
larval_counts <- read.csv("../raw_data/Copy of Larval counts - Day 1-By Family.csv")
```
Three populations of oysters were used and allowed to grow under the same conditions. I graphed the average length of the oyster shells in each population over time for the three dates it was measured.
```{r, message = FALSE}

popul_days <- group_by(PS_larvae, Population, Date)
#average length for each population
avg_l_popul <- summarize(popul_days, mean_l = mean(Average_Length), na.rm = TRUE)
#added column for days after start
avg_l_popul$Days = c(0, 14, 7, 0, 14, 7, 0, 14, 7)
#scatterplot of days passed vs length for each population with a line of best fit for each population
daysvslength <- ggplot(data = avg_l_popul, mapping = aes(x = Days, y = mean_l, group = Population)) +
  geom_point(aes(shape = Population, color = Population, size = 3)) +
  labs(x = "Days", y = "Average Shell Length (mm)") +
  scale_x_continuous(breaks = c (0, 7, 14)) +
  ggtitle("Shell Length over Time by Population")
print(daysvslength)
```

